Initial report

### 2022-11-04 initial_report.Rmd
updated analysis
added response rate and filtered for complete responses

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(viridis)

@@

# Read data
raw <- readr::read_tsv("data/ECAW_raw_data.tsv")
```

@@

# ALSPAC

@@

# Current methods

```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}
method_data <-
  raw %>% 
    select(starts_with("method_")) %>% 
    pivot_longer(
      cols = everything(),
      names_to = "variable",
      values_to = "scale",
    ) %>%
    separate(variable, into = c("name_prefix", "type")) %>% 
    group_by(type) %>% 
    count(scale) %>% 
  ungroup() %>% 
    replace_na(list(scale = "Missing")) %>% 
    mutate(
      scale = factor(scale, levels = c(
          "Never or almost never",
          "Sometimes",
          "About half the time",
          "Most of the time",
          "Always or almost always",
          "Missing",
          "I don't understand the question")
            ),
      type = case_when(
        type == "blind" ~ "Blind analysis",
        type == "confirmatory" ~ "Confirmatory analysis",
        type == "exploratory" ~ "Exploratory analysis",
        type == "preregistered" ~ "Preregistration",
        type == "script" ~ "Analysis script",
      )
      ) %>% 
  group_by(type) %>%
  tidyr::complete(scale, fill = list(n = 0)) %>% 
  mutate(
    percentage = n / sum(n)
  ) %>% 
  ungroup()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(viridis)
library(scales) # fto display percentages

@@

# Read data
raw <- readr::read_tsv("data/ECAW_raw_data.tsv")
# remove surveys where someone opened it, but didn't respond to any questions
raw <- raw %>% filter(progress!=0)
# number of respondents
nResponse <- raw %>% nrow()

# Filter for complete responses (I'm am maintaining the variable name "raw" only because it is used throughout the rest of the code)
raw <- raw %>% filter(finished)
#number of completed surveys
nResponseComplete <- raw %>% nrow()

invited <- 1148 # Number provided from Kyara at ALSPAC
bounced <- 54 # Number provided from Kyara at ALSPAC
received <- invited - bounced
```

# Response rate

We invited the ALSPAC mailing list to participate, which included `r invited` email addresses, of which `r bounced` bounced, leaving `r received` emails. The survey was completed `r nResponseComplete` times and partially completed `r nResponse - nResponseComplete` times. This gives a response rate for completed surveys of `r percent(nResponseComplete / received)` and a response rate for any questions `r percent(nResponse / received)`.

The median time taken for complete survey responses was `r (median(raw$duration_in_seconds) / 60) %>% round(1)` minutes (IQR: `r (quantile(raw$duration_in_seconds, .25) / 60) %>% round(1)` - `r (quantile(raw$duration_in_seconds, .75) / 60) %>% round(1)`)

@@

# Current practices

```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}
method_data <-
  raw %>% 
    select(starts_with("method_")) %>% 
    pivot_longer(
      cols = everything(),
      names_to = "variable",
      values_to = "scale",
    ) %>%
    separate(variable, into = c("name_prefix", "type")) %>% 
    group_by(type) %>% 
    count(scale) %>% 
  ungroup() %>% 
    replace_na(list(scale = "Missing")) %>% 
    mutate(
      scale = factor(scale, levels = c(
          "Never or almost never",
          "Sometimes",
          "About half the time",
          "Most of the time",
          "Always or almost always",
          "Missing",
          "I don't understand the question")
            ),
      type = case_when(
        type == "blind" ~ "Blind the data analyst",
        type == "confirmatory" ~ "Contain confirmatory analysis",
        type == "exploratory" ~ "Contain exploratory analysis",
        type == "preregistered" ~ "Are preregistered",
        type == "script" ~ "Share analysis scripts",
      )
      ) %>% 
  group_by(type) %>%
  tidyr::complete(scale, fill = list(n = 0)) %>% 
  mutate(
    percentage = n / sum(n)
  ) %>% 
  ungroup()

# ALSPAC and ECAWs

@@
